Learning CNN filters from user-drawn image makers for coconut-tree image classification

### 2020-06-13 main.tex
Updates from Overleaf

\usepackage[pdftex]{graphicx}
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
\usepackage{comment}
\usepackage{float}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{siunitx}
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{calc}

@@

\begin{figure*}
  \centering
  \subfloat{\includegraphics[width=.13\linewidth]{figures/qualitative/ours/upper-coco-108.png}
  }
  ~
  \subfloat{\includegraphics[width=.13\linewidth]{figures/qualitative/ours/upper-coco-2473.png}
  }
  ~
  \subfloat{\includegraphics[width=.13\linewidth]{figures/qualitative/ours/upper-non_coco-506.png}
  }
  ~
  \subfloat{\includegraphics[width=.13\linewidth]{figures/qualitative/vgg/lower-coco-1098.png}
  }
  ~
  \subfloat{\includegraphics[width=.13\linewidth]{figures/qualitative/vgg/lower-coco-2400.png}
  }
  ~
  \subfloat{\includegraphics[width=.13\linewidth]{figures/qualitative/vgg/lower-non_coco-105.png}
  }
  \caption{Misclassified images. The first row has images misclassified by the network trained by our method, and the second row has images misclassified by VGG-16. The two first images of a row have coconut trees.}
  \label{fig:ex-classification}
\end{figure*}

>>>>

\usepackage[pdftex]{graphicx}
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
\usepackage{comment}
\usepackage{float}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{siunitx}
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{calc}
\usepackage{hyperref}

@@

\begin{figure}
  \centering
  \subfloat{\includegraphics[width=.3\linewidth]{figures/qualitative/ours/upper-coco-108.png}
  }
  ~
  \subfloat{\includegraphics[width=.3\linewidth]{figures/qualitative/ours/upper-coco-2473.png}
  }
  ~
  \subfloat{\includegraphics[width=.3\linewidth]{figures/qualitative/ours/upper-non_coco-506.png}
  }
  \\
  \subfloat{\includegraphics[width=.3\linewidth]{figures/qualitative/vgg/lower-coco-1098.png}
  }
  ~
  \subfloat{\includegraphics[width=.3\linewidth]{figures/qualitative/vgg/lower-coco-2400.png}
  }
  ~
  \subfloat{\includegraphics[width=.3\linewidth]{figures/qualitative/vgg/lower-non_coco-105.png}
  }
  \caption{Misclassified images. The first row has images misclassified by the network trained by our method, and the second row has images misclassified by VGG-16. The two first images of a row have coconut trees.}
  \label{fig:ex-classification}
\end{figure}
